### 2019-03-13 papers/journal/problem.tex
Minor updates on synthesis code

\subsection{Existential condition}
We employ two techniques to examine the existential condition. 
%
First, using the bounded model checking (BMC) technique~\cite{biere1999symbolic1, biere2003bounded}.
%
%It  represents the executions of a program symbolically and 
%
%The Bounded model checking technique
BMC is an automatic technique that performs a search for the violation of the property in the program executions whose length is bounded by some fixed integer value $w$ (\textit{unwinding depth}). 
%
The bounded execution is represented symbolically as a propositional formula and solved using a SAT solver.
% is used to check the satisfiability of the resultant propositional formula.
%
In case there is no violation for a particular depth, one can progressively increase the depth until either property is violated, the problem becomes intractable, or an upper bound of the system is reached, indicating the satisfiability of the property.
%
For our case, the unwinding depth is the length of the path of the underline graph.
%
%
For the experimentation, we restrict the check only to the elementary cycles, cycles of length one. 
%
This restriction puts an upper limit of number of node, $N$ on the length of the searched path. 
%
%
%and the upper bound is the number of nodes $N$.

>>>>

\subsection{Existential condition}
We employ two techniques to examine the existential condition. 
%
First, using the bounded model checking (BMC) technique~\cite{biere1999symbolic1, biere2003bounded}.
%
%It  represents the executions of a program symbolically and 
%
%The Bounded model checking technique
BMC is an automatic technique that performs a search for the violation of the property in the program executions whose length is bounded by some fixed positive integer value $w$ (\textit{unwinding depth}). 
%
The bounded execution is represented symbolically as a propositional formula and solved using a SAT solver.
% is used to check the satisfiability of the resultant propositional formula.
%
In case there is no violation for a particular depth, one can progressively increase the depth until either property is violated, the problem becomes intractable, or an upper bound of the system is reached, indicating the satisfiability of the property.
%
For our case, the unwinding depth is the length of the path of the underline graph.
%
%
For the experimentation, we restrict the check only to the elementary cycles; cycles of length one. 
%
This restriction puts an upper limit of number of nodes, $N$ on the length of the searched path. 
%
%
%and the upper bound is the number of nodes $N$.
